flowCore: data structures package for flow cytometry data

### 2008-03-05 inst/doc/HowTo-flowCore.Rnw
update to documentation and addition of methods
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@30380 bc3139a8-67e5-0310-9ffc-ced21a209358

Much of the more sophisticated visualization of \Rclass{flowFrame} and \Rclass{flowSet} objects, including an interface to the \Rpackage{lattice} graphics system is implemented by the \Rpackage{flowViz} package, also included as part of Bioconductor. However, \Rpackage{flowCore} does implement some basic plotting facilities using the standard \Rfunction{plot} function. The basic plot provides a simple bivariate density plot of the first two parameters:

@@

To control the parameters being plotted we can supply a \Robject{y} value in the form of a character vector:

>>>>

Much of the more sophisticated visualization of \Rclass{flowFrame} and
\Rclass{flowSet} objects, including an interface to the
\Rpackage{lattice} graphics system is implemented by the
\Rpackage{flowViz} package, also included as part of
Bioconductor. However, \Rpackage{flowCore} does implement some basic
plotting facilities using the standard \Rfunction{plot} function. The
basic plot provides a simple pairs plot of all parameters:

@@

To control the parameters being plotted we can supply a \Robject{y}
value in the form of a character vector. If we choose exactly two
parameters this will create a bivariate density plot.
